### 2024-11-17 README.Rmd
reduce_to optional for reduce_dimensionality

find_nearest(glove_twitter_25d, "dog", 5L, sim_func = cos_sim)
```

@@

```{r}
valence_df_2d <- valence_embeddings_df |> 
	reduce_dimensionality(dim_1:dim_25, 2)
valence_df_2d
```
#### Normalize (Scale Embeddings to the Unit Hypersphere)

>>>>

find_nearest(glove_twitter_25d, "dog", 5L, method = "cosine")
```

@@

```{r}
valence_df_2d <- valence_embeddings_df |> 
	reduce_dimensionality(dim_1:dim_25, 2)
valence_df_2d
```
`reduce_dimensionality()` can also be used to apply the same rotation other embeddings not used to find the principle components.

```{r}
new_embeddings <- predict(glove_twitter_25d, c("new", "strange"))

# get rotation with `output_rotation = TRUE`
valence_rotation_2d <- valence_embeddings_df |> 
	reduce_dimensionality(dim_1:dim_25, 2, output_rotation = TRUE)

# apply the same rotation to new embeddings
new_with_valence_rotation <- new_embeddings |> 
	reduce_dimensionality(custom_rotation = valence_rotation_2d)
new_with_valence_rotation
```

#### Normalize (Scale Embeddings to the Unit Hypersphere)
